Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-07-28 literature/paper_draft.qmd
outline for tourism section

# Empirical Analysis

-   Comparative analysis of forecast performance using different covariance estimators on real-life dataset.

>>>>

# Forecasting Australian Domestics Tourism

- Description
- Hierarchy Description
- Models and Cross-validation 
- Structural change after 2016 (slight upward trend)
- Results over entire data set and excluding 2016 onwards
- Next steps:
  - Incorporate tourism setting into current DGP
  - Explore how to tackle structural change in MinT
